% This is just to make sure that if it goes onto multiple pages that
% it will only be on odd pages.
\afterpage{\cleardoublepage}
% Some people have had problems with needing a little more space or a little less space right before the body of the abstract. If you have that problem, you can uncomment the next line, and either add or take away space manually (negative spaces are OK).
%\vspace*{-0.05in}
% The abstract is a summary of the dissertation, thesis, or selected project with emphasis on the findings of the study.  The abstract must not exceed 1 page in length.  It should be printed in the same font and size as the rest of the work.  The abstract precedes the acknowledgments page and the body of the work.
Though multirotor unmanned aerial vehicles (UAVs) have become widely used 
during the past decade, challenges in autonomy have prevented their
widespread use when moving vehicles act as their base stations.
% from moving vehicles.
Emerging use cases including maritime
surveillance, package delivery and convoy support require UAVs to autonomously
land onto moving vehicles in potentially challenging weather
conditions.
This thesis presents improved solutions to both the state estimation and
control problems that must be solved
to enable robust, autonomous landing of multirotor UAVs onto moving vehicles.

Current state-of-the-art UAV landing systems depend on the detection of visual
fiducial markers placed on the landing target vehicle. However, in challenging
weather conditions, these fiducial markers may be undected for significant
periods of time.
This thesis demonstrates a state estimation algorithm that tracks and estimates
the locations of unknown visual features on the target vehicle.
Experimental results show that this method significantly improves the estimation of the
state of the target vehicle while the fiducial marker is not detected.
% This thesis demonstrates a state estimation algorithm that tracks
% and estimates the locations of unknown visual features on the target vehicle to
% improve the estimation
% of the state of the target vehicle
% when the fiducial marker is not detected.
% addition to the fiducial marker.
% Current state-of-the-art UAV landing systems depend on visual fiducial markers
% which serve as the landing pad for the UAV on the moving vehicle. However, in challenging weather
% conditions, these fiducial markers may be undetected by the UAV for significant
% periods of time. This thesis details a state estimation algorithm that tracks
% and estimates the locations of unknown visual features on the landing vehicle in
% addition to the fiducial marker. Simulation and hardware experiments described
% in this thesis demonstrate that using these additional visual features results in
% accurate and consistent state estimates of the landing vehicle even when the
% fiducial marker is undetected for long durations.

This thesis also describes an improved control scheme that enables a multirotor
UAV to accurately track a time-dependent trajectory. Rooted in Lie theory, this
controller computes the optimal control signal based on an error-state
formulation of the UAV dynamics.
% similar to that used in state estimation.
Simulation and hardware experiments of this control scheme show its
accuracy and computational efficiency, making it a viable solution for use in a
robust landing system.
