% This is just to make sure that if it goes onto multiple pages that
% it will only be on odd pages. If yours is more than two pages, then
% you'll have to add more of these later in this file
\afterpage{\cleardoublepage}
%
% Students may use the acknowledgments page to express appreciation for
% the committee members, friends, or family who provided assistance in
% research, writing, or technical aspects of the dissertation, thesis,
% or selected project.  Acknowledgments should be simple and in good
% taste.
I would first like to thank Dr. McLain for introducing me to the world of robotics. I
don't know if I ever would have found this passion of mine if not for him. I would also
like to thank Dr. McLain for mentoring me throughout my college career. His life
advice and example have also made permanent impacts to many
aspects of my life outside of engineering.

I would like to acknowledge the National Science Foundation for funding
the research that is described in this thesis. I would also like to acknowledge
Gaemus Collins, Adam Jaffe, and Aubrey Clausse at Planck Aerosystems who provided valuable insights and feedback
on my research.

I would like to thank the members of the MAGICC lab that I
have had the privelege to associate with every day. Thank you for collaborating
with me, helping me, and teaching me. I consider myself lucky to have had the
opportunity to work with each of you.

I would especially like to acknowledge my parents for supporting and
encouraging me in my education and for teaching me important values of hard
work, perserverance and positivity. Most of all, I would like to thank my wife, Emilie, for
her continous love and support.
