\chapter{Formatting Guidelines for Thesis}
\label{apdx:appendixb}

This appendix outlines the required formatting for theses and dissertations. While the \LaTeX\ template takes care of most of these automatically, it is the student's responsibility to ensure that all formatting requirements are incorporated in the document.

\section{Font} Times New Roman 12 pt. throughout text and 10 or 11 point for tables and figures.

\section{Margins}
\begin{itemize}
\item Preliminary Pages (Title page, Abstract page(s), Acknowledgment page, Table of Contents, List of Figures, List of Tables):
1 inch on all sides
\item Body Pages, beginning with Introduction:
1 inch on all sides
\item Chapter title pages, Appendix title page, Reference title page:
2 inches at top,
1 inch at bottom and sides
\end{itemize}

\section{Printing}
\begin{itemize}
\item Single-sided: Title page, Abstract page(s), Acknowledgment page
\item Two-sided:  Table of Contents, List of Figures, List of Tables, Body, Appendix, References
\end{itemize}
Note:  Table of Contents, List of Figures, List of Tables, Chapter title pages, References and Appendix pages must begin on the front side of a page.

\section{Page Numbering}
\begin{itemize}
\item	Page numbers are centered at the bottom of the page.
\item	Counting begins with the Title page; however, back pages are not counted until the Table of Contents.
\item	Page numbers do not appear on the page until the Table of Contents (v).
\item	Use Roman Numerals (v, vi, vii, ...) for the Table of Contents page and the pages thereafter until Chapter 1.  
\item	Use Arabic numbers (1, 2, 3 ...) beginning with Chapter 1. 
\item	Be sure numbers appear on all blank back pages once numbering begins.
\end{itemize}

\section{Spacing}
\begin{itemize}
\item	Double-space text of body.
\item	Single-space abstract, captions, quotes, long chapter titles, headings, and subheadings.
\item	Table of Contents, List of Figures, List of Tables, and References can be single-spaced or double spaced.
\item	Double-space three times after chapter titles (48 pts).
\item	Double-space twice before subheadings (24 pts). 
\item	Double-space once after subheadings (0 pts). 
\item	Double-space once between two subheadings (0 pts). 
\item	Double-space twice before and after figures (24 pts).
\item	Double-space twice before and after tables (24 pts).
\item	Double-space once before and after equations (0 pts).
\item	Do not leave a single line of text, a single-line equation, or a subheading alone on the top (widow) or bottom (orphan) of a page.
\item	Do not leave more than about 5 lines of white space remaining on a page unless it’s the end of a chapter.
\end{itemize}

\section{Figures}
\begin{itemize}
\item	Figures are normally diagrams, graphs, maps, or charts.
\item	Center figures on the page.
\item	Center captions below the figure. If two lines are needed, the caption should be left justified at margin.
\item	A figure should be placed after the paragraph of reference.  If it will not fit on the same page, continue the text and place the figure on the next page.
\end{itemize}

\section{Tables}
\begin{itemize}
\item	Tables contain numerical or statistical information.
\item	Center tables on the page.
\item	Center captions above the table.  If more than one line is needed, center the lines in an inverted pyramid:                                                          
\begin{center}Table 6.3 Comparison of roll rotation plots when node was displaced,\\
 and an X-direction off-axis force was applied.\end{center}
\item	If placed in the landscape position, the top of the table should be on the left side of the page, with the caption above the table.  The page number is placed in the standard location.
\end{itemize}